Bioconductor workflow for single-cell RNA-seq data analysis: dimensionality reduction, clustering, and pseudotime ordering

### 2017-06-18 workflow/workflow.Rmd
reproducible report

```{r parallel}
runZinb <- TRUE
runClus <- TRUE
NCORES <- 7
mysystem = Sys.info()[['sysname']]
if (mysystem == 'Darwin'){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == 'Linux'){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print('Please change this to allow parallel computing')
  register(SerialParam())
}
```

>>>>

```{r parallel}
runZinb <- TRUE
runClus <- TRUE
NCORES <- 2
mysystem = Sys.info()[['sysname']]
if (mysystem == 'Darwin'){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == 'Linux'){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print('Please change this to allow parallel computing')
  register(SerialParam())
}
```
